Implementation of poloidal density variation in collision operator

### 2019-03-05 doc/manual/version3/outputParameters.tex
Substantial revision to manual

\newcommand{\outputparam}[4]{{\setlength{\parindent}{0cm} {\ttfamily \bfseries \hypertarget{#1}{#1}}\\{\it Type}: #2\\{\it Available when}: #3\\{\it Meaning}: #4}}
\newcommand{\outputparamWithUnderscore}[5]{{\setlength{\parindent}{0cm} {\ttfamily \bfseries \hypertarget{#2}{#1}}\\{\it Type}: #3\\{\it Available when}: #4\\{\it Meaning}: #5}}
\newcommand{\underscoreparlink}[2]{{\ttfamily \hyperlink{#2}{#1}}}

In this chapter we describe output parameters which are available in the \sfincs~output file \parlink{outputFileName} after a %successful 
\sfincs~run. 
The output is in the \HDF~format, and the output can be looked at e.g. by using the {\ttfamily h5dump} command on Linux. 
Note that all parameters in the output file are case-sensitive. 
Moreover, many of the input parameters in chapter~\ref{ch:input} also exist in the output file and we refrain from repeating them here.

\section{Convergence and test parameters}

@@

\outputparam{didNonlinearCalculationConverge}
{integer}
{\parlink{RHSMode} == 1, \parlink{solveSystem} == \true, \parlink{includePhi1} == \true and \parlink{finished} available.}
{If this variable is \true~the nonlinear iteration has converged. Interpret this Boolean data by comparing to \parlink{integerToRepresentTrue}/\parlink{integerToRepresentFalse}.}

@@

\outputparam{lambda}
{real}
{\parlink{RHSMode} == 1, \parlink{solveSystem} == \true and \parlink{includePhi1} == \true.}
{Lagrange multiplier associated with the constraint that $\left\langle \Phi_1\right\rangle = 0$, which is included in the quasineutrality equation. %Should be within machine precision of 0.
This parameter should come out as negligible in quasineutrality, e.g. its size should be significantly smaller than the maximum charge density of the plasma species $Z_s n_s$.
\todo{Is this correct?}}

@@

\outputparam{NIterations}
{integer}
{\parlink{RHSMode} == 1 and \parlink{solveSystem} == \true.}
{Number of iterations in the nonlinear calculation. (In a linear calculation this will be 1.)}

@@

\section{Radial fluxes and flows}

@@

For the radial flux of each quantity (particle, momentum and energy), and for each radial coordinate, there is an output quantity associated with the zeroth-order $f_{s0}$ or with the full distribution function $f_s = f_{s0} + f_{s1}$, and there is also a quantity associated with the radial magnetic drift, with the radial $\bm{E} \times \bm{B}$-drift or with the total drift $\bm{v}_{ds} = \bm{v}_{ms} + \bm{v}_{E}$. Here we only present all possible combinations for the particle flux, but the pattern is the same for the momentum and energy flux.

@@

\outputparamWithUnderscore{particleFlux\_vd\_psiHat}
{particleFlux_vd_psiHat}
{$\text{\ttfamily Nspecies} \times \text{\ttfamily NIterations}$ matrix of reals}
{\parlink{RHSMode} == 1, \parlink{solveSystem} == \true and \parlink{includePhi1} == \true.}
{$\displaystyle \text{\ttfamily particleFlux\_vd\_psiHat} = \frac{\bar{R}}{\bar{n} \bar{v}} \left\langle \int d^3v f_s \, \bm{v}_{ds} \cdot \nabla \hat{\psi}\right\rangle$ for all plasma species. The final result is in the last index corresponding to the last nonlinear iteration.}

@@

\outputparamWithUnderscore{particleFlux\_vm\_psiHat}
{particleFlux_vm_psiHat}
{$\text{\ttfamily Nspecies} \times \text{\ttfamily NIterations}$ matrix of reals}
{\parlink{RHSMode} == 1 and \parlink{solveSystem} == \true.}
{$\displaystyle \text{\ttfamily particleFlux\_vm\_psiHat} = \frac{\bar{R}}{\bar{n} \bar{v}} \left\langle \int d^3v f_s \, \bm{v}_{ms} \cdot \nabla \hat{\psi}\right\rangle$ for all plasma species. The final result is in the last index corresponding to the last nonlinear iteration.}

@@

\outputparamWithUnderscore{particleFlux\_vE\_psiHat}
{particleFlux_vE_psiHat}
{$\text{\ttfamily Nspecies} \times \text{\ttfamily NIterations}$ matrix of reals}
{\parlink{RHSMode} == 1, \parlink{solveSystem} == \true and \parlink{includePhi1} == \true.}
{$\displaystyle \text{\ttfamily particleFlux\_vE\_psiHat} = \frac{\bar{R}}{\bar{n} \bar{v}} \left\langle \int d^3v f_s \, \bm{v}_{E} \cdot \nabla \hat{\psi}\right\rangle$ for all plasma species. The final result is in the last index corresponding to the last nonlinear iteration.}

@@

\outputparamWithUnderscore{particleFlux\_vm0\_psiHat}
{particleFlux_vm0_psiHat}
{$\text{\ttfamily Nspecies} \times \text{\ttfamily NIterations}$ matrix of reals}
{\parlink{RHSMode} == 1 and \parlink{solveSystem} == \true.}
{$\displaystyle \text{\ttfamily particleFlux\_vm0\_psiHat} = \frac{\bar{R}}{\bar{n} \bar{v}} \left\langle \int d^3v f_{s0} \, \bm{v}_{ms} \cdot \nabla \hat{\psi}\right\rangle$ for all plasma species. The final result is in the last index corresponding to the last nonlinear iteration. This variable should cancel \underscoreparlink{particleFlux\_vE0\_psiHat}{particleFlux_vE0_psiHat} in the last nonlinear iteration since $f_{s0}$ cannot drive radial transport (i.e. in a linear calculations this quantity should be 0 to high precision unless there is a radial current in the magnetic equilibrium).}

@@

\outputparamWithUnderscore{particleFlux\_vE0\_psiHat}
{particleFlux_vE0_psiHat}
{$\text{\ttfamily Nspecies} \times \text{\ttfamily NIterations}$ matrix of reals}
{\parlink{RHSMode} == 1, \parlink{solveSystem} == \true and \parlink{includePhi1} == \true.}
{$\displaystyle \text{\ttfamily particleFlux\_vE0\_psiHat} = \frac{\bar{R}}{\bar{n} \bar{v}} \left\langle \int d^3v f_{s0} \, \bm{v}_{E} \cdot \nabla \hat{\psi}\right\rangle$ for all plasma species. The final result is in the last index corresponding to the last nonlinear iteration. This variable should cancel \underscoreparlink{particleFlux\_vm0\_psiHat}{particleFlux_vm0_psiHat} in the last nonlinear iteration since $f_{s0}$ cannot drive radial transport.}

@@

\outputparamWithUnderscore{particleFlux\_vd1\_psiHat}
{particleFlux_vd1_psiHat}
{$\text{\ttfamily Nspecies} \times \text{\ttfamily NIterations}$ matrix of reals}
{\parlink{RHSMode} == 1, \parlink{solveSystem} == \true and \parlink{includePhi1} == \true.}
{$\displaystyle \text{\ttfamily particleFlux\_vd1\_psiHat} = \text{\ttfamily particleFlux\_vm\_psiHat}~+~\text{\ttfamily particleFlux\_vE0\_psiHat}$. The rationale for defining this quantity is that (at least for $E_r = 0$) it gives the particle flux that would be expected if \parlink{includePhi1} == \false.}

@@

\outputparamWithUnderscore{particleFlux\_v\textcolor{magenta}{XN}\_\textcolor{magenta}{Y}}
{particleFlux_vXN_Y}
{$\text{\ttfamily Nspecies} \times \text{\ttfamily NIterations}$ matrix of reals}
{See above for various $\textcolor{magenta}{XN}$.}
{For different options of $\textcolor{magenta}{XN}$ see output {\ttfamily particleFlux} parameters defined above. 
For different options of $\textcolor{magenta}{Y}$ see flux-surface labels (section~\ref{sec:radialCoordinates}). 
$\displaystyle \text{\ttfamily particleFlux\_v\textcolor{magenta}{XN}\_\textcolor{magenta}{Y}} = \frac{\bar{R}}{\bar{n} \bar{v}} \left\langle \int d^3v f_{s\textcolor{magenta}{N}} \, \bm{v}_{\textcolor{magenta}{X}s} \cdot \nabla \textcolor{magenta}{Y}\right\rangle$ for all plasma species. The final result is in the last index corresponding to the last nonlinear iteration.}

@@

\outputparamWithUnderscore{momentumFlux\_v\textcolor{magenta}{XN}\_\textcolor{magenta}{Y}}
{momentumFlux_vXN_Y}
{$\text{\ttfamily Nspecies} \times \text{\ttfamily NIterations}$ matrix of reals}
{See above for various $\textcolor{magenta}{XN}$.}
{For different options of $\textcolor{magenta}{XN}$ see  
\underscoreparlink{particleFlux\_v\textcolor{magenta}{XN}\_\textcolor{magenta}{Y}}{particleFlux_vXN_Y}.
For different options of $\textcolor{magenta}{Y}$ see flux-surface labels (section~\ref{sec:radialCoordinates}). 
$\displaystyle \text{\ttfamily momentumFlux\_v\textcolor{magenta}{XN}\_\textcolor{magenta}{Y}} = \frac{\bar{R}}{\bar{n} \bar{v}^2 \bar{B} \bar{m}} \left\langle \int d^3v f_{s\textcolor{magenta}{N}} \, B m_s v_{\|} \bm{v}_{\textcolor{magenta}{X}s} \cdot \nabla \textcolor{magenta}{Y}\right\rangle$ for all plasma species. The final result is in the last index corresponding to the last nonlinear iteration.}

@@

\outputparamWithUnderscore{heatFlux\_v\textcolor{magenta}{XN}\_\textcolor{magenta}{Y}}
{heatFlux_vXN_Y}
{$\text{\ttfamily Nspecies} \times \text{\ttfamily NIterations}$ matrix of reals}
{See above for various $\textcolor{magenta}{XN}$.}
{For different options of $\textcolor{magenta}{XN}$ see  
\underscoreparlink{particleFlux\_v\textcolor{magenta}{XN}\_\textcolor{magenta}{Y}}{particleFlux_vXN_Y}.
For different options of $\textcolor{magenta}{Y}$ see flux-surface labels (section~\ref{sec:radialCoordinates}). 
$\displaystyle \text{\ttfamily heatFlux\_v\textcolor{magenta}{XN}\_\textcolor{magenta}{Y}} = \frac{\bar{R}}{\bar{n} \bar{v}^3 \bar{m}} \left\langle \int d^3v f_{s\textcolor{magenta}{N}} \, \frac{m_s v^2}{2} \bm{v}_{\textcolor{magenta}{X}s} \cdot \nabla \textcolor{magenta}{Y}\right\rangle$ for all plasma species. The final result is in the last index corresponding to the last nonlinear iteration.}

@@

\outputparam{flow}
{$\text{\ttfamily Nzeta} \times \text{\ttfamily Ntheta} \times \text{\ttfamily Nspecies} \times \text{\ttfamily NIterations}$ matrix of reals}
{\parlink{RHSMode} == 1 and \parlink{solveSystem} == \true.}
{$\displaystyle \text{\ttfamily flow} =  \frac{1}{\bar{n} \bar{v}} \int d^3v \, v_{\|} f_s$.}

@@

\outputparam{velocityUsingFSADensity}
{$\text{\ttfamily Nzeta} \times \text{\ttfamily Ntheta} \times \text{\ttfamily Nspecies} \times \text{\ttfamily NIterations}$ matrix of reals}
{\parlink{RHSMode} == 1 and \parlink{solveSystem} == \true.}
{{\ttfamily velocityUsingFSADensity} =  \parlink{flow}~/~\parlink{nHats}.}

@@

\outputparam{velocityUsingTotalDensity}
{$\text{\ttfamily Nzeta} \times \text{\ttfamily Ntheta} \times \text{\ttfamily Nspecies} \times \text{\ttfamily NIterations}$ matrix of reals}
{\parlink{RHSMode} == 1 and \parlink{solveSystem} == \true.}
{{\ttfamily velocityUsingTotalDensity} =  \parlink{flow}~/~\parlink{totalDensity}.}

@@

\outputparam{MachUsingFSAThermalSpeed}
{$\text{\ttfamily Nzeta} \times \text{\ttfamily Ntheta} \times \text{\ttfamily Nspecies} \times \text{\ttfamily NIterations}$ matrix of reals}
{\parlink{RHSMode} == 1 and \parlink{solveSystem} == \true.}
{{\ttfamily MachUsingFSAThermalSpeed} =  (\parlink{mHats}~/~\parlink{THats})${}^{1/2}$~$\cdot$~\parlink{flow}~/~\parlink{nHats}.}

@@

\outputparam{FSABFlow}
{$\text{\ttfamily Nspecies} \times \text{\ttfamily NIterations}$ matrix of reals}
{\parlink{RHSMode} == 1 and \parlink{solveSystem} == \true.}
{$\displaystyle \text{\ttfamily FSABFlow} =  \frac{1}{\bar{v} \bar{B} \bar{n}} \left\langle B \int d^3v \, v_{\|} f_s \right\rangle$.}

@@

\outputparam{FSABVelocityUsingFSADensity}
{$\text{\ttfamily Nspecies} \times \text{\ttfamily NIterations}$ matrix of reals}
{\parlink{RHSMode} == 1 and \parlink{solveSystem} == \true.}
{{\ttfamily FSABVelocityUsingFSADensity} =  \parlink{FSABFlow}~/~\parlink{nHats}.}

@@

\outputparam{FSABVelocityUsingFSADensityOverB0}
{$\text{\ttfamily Nspecies} \times \text{\ttfamily NIterations}$ matrix of reals}
{\parlink{RHSMode} == 1 and \parlink{solveSystem} == \true.}
{{\ttfamily FSABVelocityUsingFSADensityOverB0} =  ($\bar{B}$~/~$B_0$)~$\cdot$~\parlink{FSABFlow}~/~\parlink{nHats}.}

@@

\outputparam{FSABVelocityUsingFSADensityOverRootFSAB2}
{$\text{\ttfamily Nspecies} \times \text{\ttfamily NIterations}$ matrix of reals}
{\parlink{RHSMode} == 1 and \parlink{solveSystem} == \true.}
{{\ttfamily FSABVelocityUsingFSADensityOverRootFSAB2} =  (1~/~\parlink{nHats})~$\cdot$~\parlink{FSABFlow}~/~(\parlink{FSABHat2})${}^{1/2}$.}

@@

\outputparam{jHat}
{$\text{\ttfamily Nzeta} \times \text{\ttfamily Ntheta} \times \text{\ttfamily NIterations}$ matrix of reals}
{\parlink{RHSMode} == 1 and \parlink{solveSystem} == \true.}
{$\displaystyle \text{\ttfamily jHat} = \frac{\bm{j} \cdot \bm{b}}{e \bar{n} \bar{v}} = \frac{1}{e \bar{n} \bar{v}} \sum_s Z_s e \int d^3v \, v_{\|} f_s = \sum_s Z_s \cdot \text{\parlink{flow}}_s$.}

@@

\outputparam{FSABjHat}
{$\text{\ttfamily NIterations}$ array of reals}
{\parlink{RHSMode} == 1 and \parlink{solveSystem} == \true.}
{$\displaystyle \text{\ttfamily FSABjHat} =  \sum_s Z_s \cdot \text{\parlink{FSABFlow}}_s$.}

>>>>

\newcommand{\outputparam}[4]{{\setlength{\parindent}{0cm} {\ttfamily \bfseries \hypertarget{#1}{#1}}\\{\it Type}: #2\\{\it Available when}: #3\\{\it Meaning}: #4}}
\newcommand{\outputparamWithUnderscore}[5]{{\setlength{\parindent}{0cm} {\ttfamily \bfseries \hypertarget{#2}{#1}}\\{\it Type}: #3\\{\it Available when}: #4\\{\it Meaning}: #5}}
%\newcommand{\underscoreparlink}[2]{{\ttfamily \hyperlink{#2}{#1}}} %%Moved this to SFINCSUserManual.tex

In this chapter we describe output parameters which are available in the \sfincs~output file (specified by \parlink{outputFileName}) after a %successful 
\sfincs~run. 
The output is in the \HDF~format, and the output can be looked at e.g. by using the {\ttfamily h5dump} command on Linux. 
Note that all parameters in the output file are case-sensitive. 
Moreover, many of the input parameters in chapter~\ref{ch:input} also exist in the output file and we refrain from repeating them here.

\section{Convergence and test parameters}
\label{sec:ConvergenceAndTestParameters}

@@

\outputparam{didNonlinearCalculationConverge}
{integer}
{\parlink{RHSMode} == 1, \parlink{solveSystem} == \true, \parlink{includePhi1} == \true, \parlink{readExternalPhi1} == \false and \parlink{finished} available.}
{If this variable is \true~the nonlinear iteration has converged. Interpret this Boolean data by comparing to \parlink{integerToRepresentTrue}/\parlink{integerToRepresentFalse}.}

@@

\outputparam{lambda}
{real}
{\parlink{RHSMode} == 1, \parlink{solveSystem} == \true, \parlink{includePhi1} == \true and \parlink{readExternalPhi1} == \false}
{Lagrange multiplier associated with the constraint that $\left\langle \Phi_1\right\rangle = 0$, which is included in the quasineutrality equation. %Should be within machine precision of 0.
This parameter should come out as negligible in quasineutrality, e.g. its size should be significantly smaller than the maximum charge density of the plasma species $Z_s n_s$.
%\todo{Is this correct?}
}

@@

\outputparam{NIterations}
{integer}
{\parlink{RHSMode} == 1 and \parlink{solveSystem} == \true}
{Number of iterations in the nonlinear calculation. (In a linear calculation this will be 1.)}

@@

\section{Radial fluxes and flows}
\label{sec:RadialFluxesAndFlows}

@@

For the radial flux of each quantity (particle, momentum and energy), and for each radial coordinate, there is an output quantity associated with the zeroth-order $f_{s0}$ or with the full distribution function $f_s = f_{s0} + f_{s1}$, and there is also a quantity associated with the radial magnetic drift, with the radial $\bm{E} \times \bm{B}$-drift or with the total drift $\bm{v}_{ds} = \bm{v}_{ms} + \bm{v}_{E}$. Here we only present all possible combinations for the particle flux, but the pattern is the same for the momentum and energy flux. 
%
\subsubsection{Classical fluxes}
%
The classical flux is often neglected as smaller than the neoclassical flux. However, in a stellarator that has been optimized to have a low ratio of parallel to perpendicular current (like W7-X), the classical flux can be of the same size as the neoclassical (particularly if the collisionality is large) \cite{Buller2018}. 
\sfincs~calculates the radial classical particle and heat fluxes, using the same normalizations as for the corresponding neoclassical fluxes. 
Note that the classical fluxes (in contrast to the neoclassical) depend on the gyro-phase dependent part of the distribution function. 
However, the first-order gyro-phase dependent part of the distribution function does not depend on the solution to the drift-kinetic equation in \sfincs, and the classical fluxes can thus be calculated to required order even without solving it. 
The classical fluxes do depend on $\Phi_1$ so if the quasi-neutrality equation is solved the fluxes will depend on the solution to the system of equations.

@@

\outputparamWithUnderscore{particleFlux\_vd\_psiHat}
{particleFlux_vd_psiHat}
{%$\text{\ttfamily Nspecies} \times \text{\ttfamily NIterations}$ 
\parlink{Nspecies}~$\times$~\parlink{NIterations} matrix of reals}
{\parlink{RHSMode} == 1, \parlink{solveSystem} == \true and \parlink{includePhi1} == \true}
{$\displaystyle \text{\ttfamily particleFlux\_vd\_psiHat} = \frac{\bar{R}}{\bar{n} \bar{v}} \left\langle \int d^3v f_s \, \bm{v}_{ds} \cdot \nabla \hat{\psi}\right\rangle$ for all plasma species. The final result is in the last index corresponding to the last nonlinear iteration.}

@@

\outputparamWithUnderscore{particleFlux\_vm\_psiHat}
{particleFlux_vm_psiHat}
{\parlink{Nspecies}~$\times$~\parlink{NIterations} matrix of reals}
{\parlink{RHSMode} == 1 and \parlink{solveSystem} == \true}
{$\displaystyle \text{\ttfamily particleFlux\_vm\_psiHat} = \frac{\bar{R}}{\bar{n} \bar{v}} \left\langle \int d^3v f_s \, \bm{v}_{ms} \cdot \nabla \hat{\psi}\right\rangle$ for all plasma species. The final result is in the last index corresponding to the last nonlinear iteration.}

@@

\outputparamWithUnderscore{particleFlux\_vE\_psiHat}
{particleFlux_vE_psiHat}
{\parlink{Nspecies}~$\times$~\parlink{NIterations} matrix of reals}
{\parlink{RHSMode} == 1, \parlink{solveSystem} == \true and \parlink{includePhi1} == \true}
{$\displaystyle \text{\ttfamily particleFlux\_vE\_psiHat} = \frac{\bar{R}}{\bar{n} \bar{v}} \left\langle \int d^3v f_s \, \bm{v}_{E} \cdot \nabla \hat{\psi}\right\rangle$ for all plasma species. The final result is in the last index corresponding to the last nonlinear iteration.}

@@

\outputparamWithUnderscore{particleFlux\_vm0\_psiHat}
{particleFlux_vm0_psiHat}
{\parlink{Nspecies}~$\times$~\parlink{NIterations} matrix of reals}
{\parlink{RHSMode} == 1 and \parlink{solveSystem} == \true}
{$\displaystyle \text{\ttfamily particleFlux\_vm0\_psiHat} = \frac{\bar{R}}{\bar{n} \bar{v}} \left\langle \int d^3v f_{s0} \, \bm{v}_{ms} \cdot \nabla \hat{\psi}\right\rangle$ for all plasma species. The final result is in the last index corresponding to the last nonlinear iteration. This variable should cancel \underscoreparlink{particleFlux\_vE0\_psiHat}{particleFlux_vE0_psiHat} in the last nonlinear iteration since $f_{s0}$ cannot drive radial particle transport (in a calculation without $\Phi_1$ this quantity should be 0 to high precision unless there is a radial current in the magnetic equilibrium),\newline i.e. $\displaystyle \text{\ttfamily particleFlux\_vm0\_psiHat} = - \text{\ttfamily particleFlux\_vE0\_psiHat}$.}

@@

\outputparamWithUnderscore{particleFlux\_vE0\_psiHat}
{particleFlux_vE0_psiHat}
{\parlink{Nspecies}~$\times$~\parlink{NIterations} matrix of reals}
{\parlink{RHSMode} == 1, \parlink{solveSystem} == \true and \parlink{includePhi1} == \true}
{$\displaystyle \text{\ttfamily particleFlux\_vE0\_psiHat} = \frac{\bar{R}}{\bar{n} \bar{v}} \left\langle \int d^3v f_{s0} \, \bm{v}_{E} \cdot \nabla \hat{\psi}\right\rangle$ for all plasma species. The final result is in the last index corresponding to the last nonlinear iteration. This variable should cancel \underscoreparlink{particleFlux\_vm0\_psiHat}{particleFlux_vm0_psiHat} in the last nonlinear iteration since $f_{s0}$ cannot drive radial particle transport, i.e. $\displaystyle \text{\ttfamily particleFlux\_vm0\_psiHat} = - \text{\ttfamily particleFlux\_vE0\_psiHat}$.}

@@

\outputparamWithUnderscore{particleFlux\_vd1\_psiHat}
{particleFlux_vd1_psiHat}
{\parlink{Nspecies}~$\times$~\parlink{NIterations} matrix of reals}
{\parlink{RHSMode} == 1, \parlink{solveSystem} == \true and \parlink{includePhi1} == \true}
{$\displaystyle \text{\ttfamily particleFlux\_vd1\_psiHat} = \text{\ttfamily particleFlux\_vm\_psiHat}~+~\text{\ttfamily particleFlux\_vE0\_psiHat}$. The rationale for defining this quantity is that (at least for $E_r = 0$) it gives the particle flux that would be expected if \parlink{includePhi1} == \false.}

@@

\outputparamWithUnderscore{classicalParticleFlux\_psiHat}
{classicalParticleFlux_psiHat}
{%$\text{\ttfamily Nspecies} \times \text{\ttfamily NIterations}$ 
\parlink{Nspecies}~$\times$~\parlink{NIterations} matrix of reals}
{\parlink{RHSMode} == 1 and \parlink{solveSystem} == \true}
{$\displaystyle \text{\ttfamily classicalParticleFlux\_psiHat} = \frac{\bar{R}}{\bar{n} \bar{v}} \frac{1}{Z_s e} \left\langle \frac{\vect{B} \times \nabla \hat{\psi}}{B^2} \cdot \vect{R}_s \right\rangle$ for all plasma species. $\displaystyle \vect{R}_s = m_s \sum_a \int d^3v \, \vect{v} C_s \left[f_s, f_a\right]$ is the friction force acting on the species. The final result is in the last index corresponding to the last nonlinear iteration.}

\outputparamWithUnderscore{particleFlux\_v\textcolor{magenta}{XN}\_\textcolor{magenta}{Y}}
{particleFlux_vXN_Y}
{\parlink{Nspecies}~$\times$~\parlink{NIterations} matrix of reals}
{See above for various $\textcolor{magenta}{XN}$}
{$\displaystyle \text{\ttfamily particleFlux\_v\textcolor{magenta}{XN}\_\textcolor{magenta}{Y}} = \frac{\bar{R}}{\bar{n} \bar{v}} \left\langle \int d^3v f_{s\textcolor{magenta}{N}} \, \bm{v}_{\textcolor{magenta}{X}s} \cdot \nabla \textcolor{magenta}{Y}\right\rangle$ for all plasma species. The final result is in the last index corresponding to the last nonlinear iteration.\newline
For different options of $\textcolor{magenta}{XN}$ see output {\ttfamily particleFlux} parameters defined above.\newline 
For different options of $\textcolor{magenta}{Y}$ see flux-surface labels (section~\ref{sec:radialCoordinates}).}

\outputparamWithUnderscore{classicalParticleFlux\_\textcolor{magenta}{Y}}
{classicalParticleFlux_Y}
{\parlink{Nspecies}~$\times$~\parlink{NIterations} matrix of reals}
{\parlink{RHSMode} == 1 and \parlink{solveSystem} == \true}
{$\displaystyle \text{\ttfamily classicalParticleFlux\_\textcolor{magenta}{Y}} = \frac{\bar{R}}{\bar{n} \bar{v}} \frac{1}{Z_s e} \left\langle \frac{\vect{B} \times \nabla \textcolor{magenta}{Y}}{B^2} \cdot \vect{R}_s \right\rangle$ for all plasma species. $\displaystyle \vect{R}_s = m_s \sum_a \int d^3v \, \vect{v} C_s \left[f_s, f_a\right]$ is the friction force acting on the species. The final result is in the last index corresponding to the last nonlinear iteration.\newline
For different options of $\textcolor{magenta}{Y}$ see flux-surface labels (section~\ref{sec:radialCoordinates}).}

\outputparamWithUnderscore{classicalParticleFluxNoPhi1\_\textcolor{magenta}{Y}}
{classicalParticleFluxNoPhi1_Y}
{\parlink{Nspecies} array of reals}
{\parlink{RHSMode} == 1}
{$\displaystyle \text{\ttfamily classicalParticleFluxNoPhi1\_\textcolor{magenta}{Y}} = \frac{\bar{R}}{\bar{n} \bar{v}} \frac{1}{Z_s e} \left\langle \frac{\vect{B} \times \nabla \textcolor{magenta}{Y}}{B^2} \cdot \vect{R}_{s,\,\mathrm{w/o}\,\Phi_1} \right\rangle$ for all plasma species. $\displaystyle \vect{R}_{s,\,\mathrm{w/o}\,\Phi_1} = m_s \sum_a \int d^3v \, \vect{v} C_s \left[f_{s,\,\mathrm{w/o}\,\Phi_1}, f_{a,\,\mathrm{w/o}\,\Phi_1}\right]$ is the friction force acting on the species, where the impact of $\Phi_1$ is neglected.\newline
For different options of $\textcolor{magenta}{Y}$ see flux-surface labels (section~\ref{sec:radialCoordinates}).}

@@

\outputparamWithUnderscore{momentumFlux\_v\textcolor{magenta}{XN}\_\textcolor{magenta}{Y}}
{momentumFlux_vXN_Y}
{\parlink{Nspecies}~$\times$~\parlink{NIterations} matrix of reals}
{See above for various $\textcolor{magenta}{XN}$}
{$\displaystyle \text{\ttfamily momentumFlux\_v\textcolor{magenta}{XN}\_\textcolor{magenta}{Y}} = \frac{\bar{R}}{\bar{n} \bar{v}^2 \bar{B} \bar{m}} \left\langle \int d^3v f_{s\textcolor{magenta}{N}} \, B m_s v_{\|} \bm{v}_{\textcolor{magenta}{X}s} \cdot \nabla \textcolor{magenta}{Y}\right\rangle$ for all plasma species. The final result is in the last index corresponding to the last nonlinear iteration.\newline
For different options of $\textcolor{magenta}{XN}$ see  
\underscoreparlink{particleFlux\_v\textcolor{magenta}{XN}\_\textcolor{magenta}{Y}}{particleFlux_vXN_Y}.\newline
For different options of $\textcolor{magenta}{Y}$ see flux-surface labels (section~\ref{sec:radialCoordinates}).}

@@

\outputparamWithUnderscore{heatFlux\_v\textcolor{magenta}{XN}\_\textcolor{magenta}{Y}}
{heatFlux_vXN_Y}
{\parlink{Nspecies}~$\times$~\parlink{NIterations} matrix of reals}
{See above for various $\textcolor{magenta}{XN}$}
{$\displaystyle \text{\ttfamily heatFlux\_v\textcolor{magenta}{XN}\_\textcolor{magenta}{Y}} = \frac{\bar{R}}{\bar{n} \bar{v}^3 \bar{m}} \left\langle \int d^3v f_{s\textcolor{magenta}{N}} \, \frac{m_s v^2}{2} \bm{v}_{\textcolor{magenta}{X}s} \cdot \nabla \textcolor{magenta}{Y}\right\rangle$ for all plasma species. The final result is in the last index corresponding to the last nonlinear iteration.\newline
For different options of $\textcolor{magenta}{XN}$ see  
\underscoreparlink{particleFlux\_v\textcolor{magenta}{XN}\_\textcolor{magenta}{Y}}{particleFlux_vXN_Y}.\newline
For different options of $\textcolor{magenta}{Y}$ see flux-surface labels (section~\ref{sec:radialCoordinates}).}

@@

\outputparamWithUnderscore{classicalHeatFlux\_\textcolor{magenta}{Y}}
{classicalHeatFlux_Y}
{\parlink{Nspecies}~$\times$~\parlink{NIterations} matrix of reals}
{\parlink{RHSMode} == 1 and \parlink{solveSystem} == \true}
{\todo{Can Stefan update the text so it is correct?}\newline
$\displaystyle \text{\ttfamily classicalHeatFlux\_\textcolor{magenta}{Y}} = \frac{\bar{R}}{\bar{n} \bar{v}} \frac{1}{Z_s e} \left\langle \frac{\vect{B} \times \nabla \textcolor{magenta}{Y}}{B^2} \cdot \vect{R}_s \right\rangle$ for all plasma species. $\displaystyle \vect{R}_s = m_s \sum_a \int d^3v \, \vect{v} C_s \left[f_s, f_a\right]$ is the friction force acting on the species. The final result is in the last index corresponding to the last nonlinear iteration.\newline
For different options of $\textcolor{magenta}{Y}$ see flux-surface labels (section~\ref{sec:radialCoordinates}).}

@@

\outputparamWithUnderscore{classicalHeatFluxNoPhi1\_\textcolor{magenta}{Y}}
{classicalHeatFluxNoPhi1_Y}
{\parlink{Nspecies} array of reals}
{\parlink{RHSMode} == 1}
{\todo{Can Stefan update the text so it is correct?}\newline
$\displaystyle \text{\ttfamily classicalHeatFluxNoPhi1\_\textcolor{magenta}{Y}} = \frac{\bar{R}}{\bar{n} \bar{v}} \frac{1}{Z_s e} \left\langle \frac{\vect{B} \times \nabla \textcolor{magenta}{Y}}{B^2} \cdot \vect{R}_{s,\,\mathrm{w/o}\,\Phi_1} \right\rangle$ for all plasma species. $\displaystyle \vect{R}_{s,\,\mathrm{w/o}\,\Phi_1} = m_s \sum_a \int d^3v \, \vect{v} C_s \left[f_{s,\,\mathrm{w/o}\,\Phi_1}, f_{a,\,\mathrm{w/o}\,\Phi_1}\right]$ is the friction force acting on the species, where the impact of $\Phi_1$ is neglected.\newline
For different options of $\textcolor{magenta}{Y}$ see flux-surface labels (section~\ref{sec:radialCoordinates}).}

@@

\outputparam{flow}
{\parlink{Nzeta}~$\times$~\parlink{Ntheta}~$\times$~\parlink{Nspecies}~$\times$~\parlink{NIterations} matrix of reals}
{\parlink{RHSMode} == 1 and \parlink{solveSystem} == \true}
{$\displaystyle \text{\ttfamily flow} =  \frac{1}{\bar{n} \bar{v}} \int d^3v \, v_{\|} f_s$.}

@@

\outputparam{velocityUsingFSADensity}
{\parlink{Nzeta}~$\times$~\parlink{Ntheta}~$\times$~\parlink{Nspecies}~$\times$~\parlink{NIterations} matrix of reals}
{\parlink{RHSMode} == 1 and \parlink{solveSystem} == \true}
{{\ttfamily velocityUsingFSADensity} =  \parlink{flow}~/~\parlink{nHats}.}

@@

\outputparam{velocityUsingTotalDensity}
{\parlink{Nzeta}~$\times$~\parlink{Ntheta}~$\times$~\parlink{Nspecies}~$\times$~\parlink{NIterations} matrix of reals}
{\parlink{RHSMode} == 1 and \parlink{solveSystem} == \true}
{{\ttfamily velocityUsingTotalDensity} =  \parlink{flow}~/~\parlink{totalDensity}.}

@@

\outputparam{MachUsingFSAThermalSpeed}
{\parlink{Nzeta}~$\times$~\parlink{Ntheta}~$\times$~\parlink{Nspecies}~$\times$~\parlink{NIterations} matrix of reals}
{\parlink{RHSMode} == 1 and \parlink{solveSystem} == \true}
{{\ttfamily MachUsingFSAThermalSpeed} =  (\parlink{mHats}~/~\parlink{THats})${}^{1/2}$~$\cdot$~\parlink{flow}~/~\parlink{nHats}.}

@@

\outputparam{FSABFlow}
{\parlink{Nspecies}~$\times$~\parlink{NIterations} matrix of reals}
{\parlink{RHSMode} == 1 and \parlink{solveSystem} == \true}
{$\displaystyle \text{\ttfamily FSABFlow} =  \frac{1}{\bar{v} \bar{B} \bar{n}} \left\langle B \int d^3v \, v_{\|} f_s \right\rangle$.}

@@

\outputparam{FSABVelocityUsingFSADensity}
{\parlink{Nspecies}~$\times$~\parlink{NIterations} matrix of reals}
{\parlink{RHSMode} == 1 and \parlink{solveSystem} == \true}
{{\ttfamily FSABVelocityUsingFSADensity} =  \parlink{FSABFlow}~/~\parlink{nHats}.}

@@

\outputparam{FSABVelocityUsingFSADensityOverB0}
{\parlink{Nspecies}~$\times$~\parlink{NIterations} matrix of reals}
{\parlink{RHSMode} == 1 and \parlink{solveSystem} == \true}
{{\ttfamily FSABVelocityUsingFSADensityOverB0} =  ($\bar{B}$~/~$B_0$)~$\cdot$~\parlink{FSABFlow}~/~\parlink{nHats}.}

@@

\outputparam{FSABVelocityUsingFSADensityOverRootFSAB2}
{\parlink{Nspecies}~$\times$~\parlink{NIterations} matrix of reals}
{\parlink{RHSMode} == 1 and \parlink{solveSystem} == \true}
{{\ttfamily FSABVelocityUsingFSADensityOverRootFSAB2} =  (1~/~\parlink{nHats})~$\cdot$~\parlink{FSABFlow}~/~(\parlink{FSABHat2})${}^{1/2}$.}
